---
title: "p8105_hw3_yq2378"
author: "Qi Yumeng"
date: "2023-10-07"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(warn = -1)  # 禁用警告
```

The goal is to do some exploration of this dataset. To that end, write a short description of the dataset, noting the size and structure of the data, describing some key variables, and giving illustrative examples of observations. Then, do or answer the following (commenting on the results of each):

How many aisles are there, and which aisles are the most items ordered from?
Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.
Make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.
Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table).



```{r}
library(p8105.datasets)
library(tidyverse)
library(ggpubr)
```

```{r}
data("instacart")
head(instacart)
```
The data has `r nrow(instacart)` observations of `r ncol(instacart)` variables, where each row in the dataset is a product from an order. `order_id` is order identifier. `user_id` is customer identifier. `order_dow` is the day of the week on which the order was placed. `order_hour_of_day` is the hour of the day on which the order was placed. `product_name` is the name of the product. `aisle` is the name of the aisle. `department` is the name of the department.

There are 134 unique aisles and fresh vegetables is the most items ordered from. Fresh fruits comes the second and packaged vegetables fruit comes the third.
```{r}
instacart %>% group_by(aisle) %>% summarise(cnt = n()) %>% arrange(desc(cnt))
```
Grouped the data by aisle and reorder the data by the number of items ordered in each aisle, we could easily see that the number of fresh vegetables and fruits are almost twice as that of packaged vegetables fruits. The least popular items are dry pasta, oil vinegars and butter.

```{r}
instacart %>% group_by(aisle) %>% summarise(cnt = n()) %>%  filter(cnt>10000) %>% 
  ggplot(aes(x = reorder(aisle, cnt), y = cnt))+ geom_bar(stat="identity") + coord_flip() +
  xlab("Aisle") + theme_pubclean()
```
The three most popular items in “baking ingredients”, “dog food care”, and “packaged vegetables fruits”
were listed below. For packaged vegetables, the hit products are Organic Baby Spinach, Organic Raspberries and Organic Blueberries. For baking ingredients, the hit products are Light Brown Sugar, 	Pure Baking Soda and Cane Sugar. For dog food care, the hit products are 	Snack Sticks Chicken & Rice Recipe Dog Treats, Organix Chicken & Brown Rice Recipe and Small Dog Biscuits
```{r}
instacart %>% filter(aisle %in% c("baking ingredients","dog food care","packaged vegetables fruits")) %>% group_by(aisle,product_name) %>% summarise(cnt = n()) %>% arrange(desc(cnt)) %>% slice(1:3)%>% arrange(desc(cnt))
```
Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table).

The table shows the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week.
```{r}
#lookup = c(0 ="Sun",1 ="Mon",2= "Tue",3="Wed",4="Thu",5="Fri",6="Sat")
df_temp = instacart %>% filter(product_name %in% c("Pink Lady Apples","Coffee Ice Cream")) %>% group_by(order_dow,product_name) %>% summarise(mean_order_hour_of_day = round(mean(order_hour_of_day),2)) %>% pivot_wider(names_from = order_dow,values_from = mean_order_hour_of_day)
names(df_temp) = c("product name","Sun","Mon","Tue","Wed","Thu","Fri","Sat")
df_temp
```